Results

### 2019-01-10 4-results-simus.Rmd
merge figures

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(method %in% c("PLR", "C+T-max"), par.model == "ADD") %>%
  barplot_causal_one(h2 = 0.8)

ggsave("figures/main-AUC-logit.pdf", scale = 1/90, width = 844, height = 872)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(grepl("C\\+T", method)) %>%
  barplot_causal_one(h2 = 0.8)

ggsave("figures/main-AUC-PRS.pdf", scale = 1/90, width = 844, height = 872)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(method %in% c("PLR", "C+T-max")) %>%
  barplot_causal_one(h2 = 0.5)

ggsave("figures/supp-AUC-logit.pdf", scale = 1/90, width = 844, height = 872)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(grepl("C\\+T", method)) %>%
  barplot_causal_one(h2 = 0.5)

ggsave("figures/supp-AUC-PRS.pdf", scale = 1/90, width = 844, height = 872)
```

>>>>

```{r}
results3.summary %>%
  filter(method %in% c("PLR", "C+T-max"), par.model == "ADD") %>%
  barplot_causal_all()

ggsave("figures/main-AUC-logit.pdf", scale = 1/110, width = 1242, height = 951)
```

```{r}
results3.summary %>%
  filter(grepl("C\\+T", method)) %>%
  barplot_causal_all()

ggsave("figures/supp-AUC-PRS.pdf", scale = 1/110, width = 1242, height = 951)
```
